Interval Probability for Fuzzy Quantum Theories

### 2016-06-05 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Add an example but still don't have intuition...

A special feature of this theory is that it discusses the relation
between non-commuting subspaces while the real-valued quantum probability
measures in definition~\ref{def:QuantumProbabilitySpace} only depend
on orthogonal (or commuting) subspaces. Thinking a physical process
which put two non-commuting spaces together... Maybe two directions
of the first spin in the two-spin system?

>>>>

Interestingly, this theory discussed the relation between non-commuting
subspaces while the real-valued quantum probability measures in definition~\ref{def:QuantumProbabilitySpace}
only depend on orthogonal (or commuting) subspaces. In order to understand
the intuition, let's go through the simplest example.

\begin{example}{[}Two-qubit quantum probability space{]} Consider
a two-qubit Hilbert space with the following subspaces:
\begin{eqnarray*}
S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
\end{eqnarray*}
 Then, their projection and non-additivity operators are 
\begin{eqnarray*}
\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
\end{eqnarray*}
We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
are
\begin{eqnarray*}
\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
\end{eqnarray*}
and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
However, I still don't have much intuition on why the probabilities
should have what kind of relations?\qed\end{example}
